tstrait: a quantitative trait simulator for ancestral recombination graphs

### 2024-03-11 paper.tex
Updates from Overleaf

\begin{figure*}[t]%
\centering
% FIXME get the sizes right here and in the notebook where we're generating
% the figure so we don't have to scale here.
\includegraphics[width=213pt]{figures/time-scaling.pdf}
\caption{\textbf{Time taken to simulate quantitative traits.} Each point
represents the mean time for 10 independent runs under different random seeds with 95\% confidence intervals plotted.
The times reported are the total CPU time required to simulate quantitative
traits on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM. The trait model
is a normal distribution with $\mu=0$, $\sigma^2=1$, $h^2=0.3$, and
$\alpha=0$. \texttt{tstrait} is used to simulate quantitative traits from ARGs simulated using \texttt{stdpopsim} with the HomSap demographic mode. For each replicate we simulate one quantitative trait with 1000 causal sites. We have compared \texttt{tstrait} against the quantitative trait simulation framework that is based on \texttt{tskit} functionalities. The comparison codes are adapted from \citep{martin2017}, and they are modified based on functionalities offered in \texttt{tskit} version 0.5.6 to speed up the computational efficiency.}\label{fig:time}
\end{figure*}
\end{document}

>>>>

\begin{figure*}[t]%
\centering
% FIXME get the sizes right here and in the notebook where we're generating
% the figure so we don't have to scale here.
\includegraphics[width=213pt]{figures/time-scaling.pdf}
\caption{\textbf{Time taken to simulate quantitative traits.} Each point
represents the mean time for 10 independent runs under different random seeds with 95\% confidence intervals plotted.
The times reported are the total CPU time required to simulate quantitative
traits on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM. The trait model
is a normal distribution with $\mu=0$, $\sigma^2=1$, $h^2=0.3$, and
$\alpha=0$. \texttt{tstrait} is used to simulate quantitative traits from ARGs simulated using \texttt{stdpopsim} with the generic piecewise constant size model in Homo Sapiens catalog. For each replicate we simulate one quantitative trait with 1000 causal sites. We have compared \texttt{tstrait} against the quantitative trait simulation framework that is based on \texttt{tskit} functionalities. The comparison codes are adapted from \citep{martin2017}, and they are modified based on functionalities offered in \texttt{tskit} version 0.5.6 to speed up the computational efficiency.}\label{fig:time}
\end{figure*}
\end{document}
